\documentclass[11pt]{letter}

\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}

\signature{Subham Paul}
\address{Kolkata, West Bengal, India \\ subhampaul011@gmail.com \\ (+91) 8768427379 \\ linkedin.com/in/subham-paul123 \\ github.com/subham-max}

\begin{document}

\begin{letter}{Hiring Team \\ Industrial Scientific (Fortive) \\ Mid-Level Full Stack Engineer}

\opening{Dear Hiring Team,}

I'm writing to apply for the Mid-Level Full Stack Engineer role at Industrial Scientific. Your mission of ending death on the job by 2050 is the kind of purpose-driven engineering work I'd genuinely value being part of, and the scope of this role -- building UIs and APIs, owning data access layers, working across AWS -- lines up closely with how I like to work as an engineer.

My background is centered on React, Next.js, and TypeScript, with 3+ years of hands-on frontend development and full-stack depth I've built over the past year in Node.js, Express, PostgreSQL, Redis, and Docker, including CI/CD pipelines deployed on AWS. At Maxbridge Solution LLP, I led a six-member engineering team delivering production systems for government and healthcare clients, including a GIS-based land mapping platform and two healthcare applications live on both major app stores with biometric authentication integration.

I want to be upfront about one gap: my production experience is in the Node.js/Express ecosystem rather than .NET and C\#. I recognize your posting lists full-stack experience with both React/Next.js and .NET C\# as a required qualification, so I understand this may not be a fit as-is. That said, my API design, Entity Framework-equivalent data-access patterns (via Drizzle ORM and raw SQL), and backend architecture experience transfer directly, and I'm confident in my ability to ramp up on C\#/.NET quickly given a strong foundation in object-oriented design and modern backend practices. I'd welcome the chance to discuss whether that trade-off works for your team.

Thank you for your time and consideration.

\closing{Sincerely,}

\end{letter}
\end{document}