%-------------------------
% Subham Paul - Resume
% ATS-friendly single column LaTeX resume
%-------------------------
\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure PDF is machine readable / ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.18in]\itemsep -2pt}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Subham Paul} \\ \vspace{4pt}
    \small
    Kolkata, West Bengal, India $|$
    \href{mailto:subhampaul011@gmail.com}{subhampaul011@gmail.com} $|$
    (+91) 8768427379 $|$
    \href{https://linkedin.com/in/subham-paul123}{linkedin.com/in/subham-paul123} $|$
    \href{https://github.com/subham-max}{github.com/subham-max} $|$
    \href{https://subham-max.netlify.app}{subham-max.netlify.app} \\
    \vspace{2pt}
    \textit{Immediate Joiner \, $|$ \, Open to Remote / Hybrid / Onsite roles across India}
\end{center}


%-----------SUMMARY-----------
\section{Professional Summary}
\small{Full-stack developer with 3+ years of experience building modern web applications using React, Next.js, and TypeScript, with strong exposure to backend integration, REST-based services, cloud deployment, and delivery automation. Delivered production systems across geospatial mapping, biometric authentication, and secure payment workflows for government, healthcare, and e-commerce clients. Known for collaborating with product and engineering stakeholders to design scalable solutions, improve code quality through testing and reviews, and ship reliable features using CI/CD, Docker, and AWS.}

\vspace{4pt}
\small{\textbf{Core Competencies:} Full Stack Development $\bullet$ React / Next.js $\bullet$ REST APIs $\bullet$ Cloud Deployment $\bullet$ CI/CD $\bullet$ Testing \& Quality $\bullet$ Team Collaboration $\bullet$ Agile Delivery}

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} TypeScript, JavaScript (ES6+), HTML5, CSS3/SCSS, SQL, Dart \\
     \textbf{Frontend Frameworks:} Angular (v17), React.js, Next.js, RxJS, Vue.js, Tailwind CSS \\
     \textbf{Backend \& APIs:} Node.js, Express.js, REST APIs, PostgreSQL, Redis, MongoDB, Firebase, Drizzle ORM \\
     \textbf{DevOps \& Cloud:} Docker, GitHub Actions, AWS (ECS), CI/CD Pipelines, Vercel, Hostinger \\
     \textbf{Specialized Technologies:} OpenLayers GIS, SHP/GeoJSON Rendering, Biometric APIs, Aadhaar Authentication, Face Recognition, OAuth2/JWT, SAP BTP Extensions \\
     \textbf{Payments:} Razorpay, CcAvenue \\
     \textbf{Testing:} Jest, Karma, Jasmine, Postman \\
     \textbf{Tools:} Git, Jira, Agile/Scrum, VS Code, IIS, Microsoft Teams \\
\section{Experience}
  \resumeSubHeadingListStart

    \item
      \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{Maxbridge Solution LLP} & Kolkata, India \\
        \textit{Frontend Developer (SD-2)} & \textit{May 2025 -- May 2026} \\
        \textit{\footnotesize Promoted from Application Developer} & \textit{\footnotesize March 2023 -- April 2025} \\
      \end{tabular*}\vspace{-7pt}
      \resumeItemListStart
        \resumeItem{Coordinated and mentored a 6-member engineering squad for the RCS Enterprise Suite; led recruitment drives and technical interviews, scaling team capacity by 40\% while maintaining 95\%+ sprint completion rates.}
        \resumeItem{Built scalable React / Next.js / TypeScript applications for enterprise workflows, integrating UI modules with secure authentication, role-based access, and backend services for 10,000+ users across state government clients.}
        \resumeItem{Delivered workflow-driven features for enterprise platforms with multi-stage approvals, reusable components, and API-driven data flows, improving reliability and maintainability across client projects.}
        \resumeItem{Developed and deployed cross-platform Flutter mobile applications (Android + iOS); integrated Razorpay and CcAvenue payment gateways with full store deployment.}
        \resumeItem{Built OpenLayers + Angular GIS modules to parse SHP files and GeoJSON for state government spatial data infrastructure planning.}
        \resumeItem{Integrated biometric hardware, Aadhaar-based authentication, and Face Recognition APIs, supporting 1,000+ daily secure employee authentications for NTPC/NSPCL (Government of India enterprises).}
        \resumeItem{Applied engineering best practices including code reviews, unit testing, performance optimization, and deployment automation to improve release quality and delivery efficiency.}
        \resumeItem{Collaborated closely with product managers, architects, and technical leads to translate business requirements into scalable, maintainable solutions.}
      \resumeItemListEnd

    \resumeSubheading
      {Rolling Arrays}{Mumbai, India}
      {Associate Consultant}{July 2022 -- December 2022}
      \resumeItemListStart
        \resumeItem{Developed custom UI enhancements within SAP SuccessFactors for enterprise HR clients, ensuring alignment with client workflows and branding guidelines.}
        \resumeItem{Built and deployed custom frontend modules via SAP BTP Extension Center, extending core Recruiting and Onboarding functionality for enterprise clients.}
        \resumeItem{Implemented data-binding logic using SAP OData APIs for real-time synchronization between custom extensions and the SuccessFactors core database.}
      \resumeItemListEnd

    \resumeSubheading
      {Ayant Software Pvt Ltd}{Kolkata, India}
      {Team Leader \textit{--- Promoted from Associate}}{January 2018 -- February 2020}
      \resumeItemListStart
        \resumeItem{Designed and administered technical screening assessments for frontend and full-stack developer candidates, evaluating proficiency across JavaScript, Angular, React, and web development fundamentals.}
        \resumeItem{Developed structured coding challenge frameworks and competency rubrics with senior engineers, standardizing the technical evaluation process and improving quality-of-hire consistency.}
        \resumeItem{Led end-to-end developer recruitment -- sourcing, screening, and interviewing -- and onboarded high-performing engineers into structured training programs, reducing time-to-productivity through clear onboarding documentation.}
        \resumeItem{Partnered with technical leads and project managers to define evolving skill requirements aligned with software delivery needs.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Key Projects}
    \resumeSubHeadingListStart

      \item
        \textbf{RCS Enterprise Suite} $|$ Office \& Co-operative Management System \hfill \href{https://its4rcs.com/}{its4rcs.com} \\
        \textit{\small Next.js, React, TypeScript, RxJS, Dynamic Forms, PDF Engine}
        \resumeItemListStart
          \resumeItem{High-security management platform for the Head of Co-operatives, built as Lead Developer of a 6-person team: custom email workflows, multi-stage approval system, RBAC, and API-driven data flows -- reduced manual processing by approximately 40\%.}
        \resumeItemListEnd

      \item
        \textbf{NTPC Sanjeevani + NSPCL Niramaya} $|$ Hospital Management System \hfill \href{https://sanjeevaninew.ntpc.co.in}{sanjeevaninew.ntpc.co.in}, \href{https://niramaya.nspcl.co.in}{niramaya.nspcl.co.in} \\
        \textit{\small Angular, Custom CMS, Biometric APIs, Aadhaar Authentication, Face Recognition}
        \resumeItemListStart
          \resumeItem{Full HMS with custom CMS and Biometric + Aadhaar + Face Recognition authentication, supporting 1,000+ daily authentications for Government of India enterprises. Live at \href{https://sanjeevaninew.ntpc.co.in}{sanjeevaninew.ntpc.co.in} and \href{https://niramaya.nspcl.co.in}{niramaya.nspcl.co.in}.}
        \resumeItemListEnd

      \item
        \textbf{Arunachal Pradesh GIS Portal} $|$ Geospatial Data Analysis \hfill \href{https://apcis.in/}{apcis.in} \\
        \textit{\small Angular, OpenLayers, GeoJSON, SHP File Rendering}
        \resumeItemListStart
          \resumeItem{SHP and GeoJSON parsing with interactive multi-layer visualization for government infrastructure planning.}
        \resumeItemListEnd

      \item
        \textbf{PHED App} $|$ Water Services Utility \hfill \textit{\small Play Store \& App Store} \\
        \textit{\small Flutter (Dart), Razorpay, CcAvenue, Cross-Platform}
        \resumeItemListStart
          \resumeItem{Dynamic form-driven mobile app with integrated secure payment gateways (Razorpay + CcAvenue), deployed live on both Android and iOS stores.}
        \resumeItemListEnd

      \item
        \textbf{Get All Book} $|$ E-Commerce Mobile Platform \hfill \textit{\small Play Store} \\
        \textit{\small Flutter (Dart), Firebase, State Management, Real-time Tracking}
        \resumeItemListStart
          \resumeItem{Full-scale e-commerce app with cart, wishlist, and real-time order tracking, live on Google Play Store.}
        \resumeItemListEnd

      \item
        \textbf{ApplyTrack} $|$ Full-Stack Portfolio Project \hfill \textit{\small In Progress} \\
        \textit{\small Next.js 15, Node.js/Express, Drizzle ORM, Neon Postgres, Upstash Redis, Docker, GitHub Actions, AWS ECS}
        \resumeItemListStart
          \resumeItem{Self-initiated full-stack application demonstrating backend and DevOps proficiency end-to-end: containerized services, automated CI/CD pipelines, cloud deployment on AWS ECS, and modern testing practices.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {St. Xavier's College, Park Street}{Kolkata, India}
      {Master of Science (M.Sc.) in Computer Science \textit{--- CGPA: 8.1/10}}{June 2020 -- August 2022}
      \resumeItemListStart
        \resumeItem{Best Project Award: COVID-19 Pandemic Prediction using Machine Learning.}
      \resumeItemListEnd
    \resumeSubheading
      {Maulana Abu Kalam Azad University of Technology}{Kolkata, India}
      {Bachelor of Computer Applications (BCA)}{May 2014 -- July 2017}
  \resumeSubHeadingListEnd

\end{document}